MCLM parameters, interactive example

### 2024-05-14 apps/Graphical_representation_interactive.qmd
Corrects computation of MIRT parameters
The multidimensional parameters must be computed with the covariance matrix instead of the correlation matrix

observeEvent(
  list(input$a_1, input$a_2, input$d, cov_matrix()),
  item_oblique({
    oblique_params <- item_M2PL() |> compute_mirt_params(
      all_of(INTERCEPT_COLKEY), starts_with(DISCR_PREFFIX), # Input parameters
      cov_matrix = corr_matrix(),                           # Input correlations
      dir_out    = c(COSINE_DIRTYPE, DEGREE_DIRTYPE)        # Output configuration
    )
    oblique_coords <- oblique_params |> compute_mirt_coords(
      D, MDISC, starts_with(COSINE_DIRTYPE),
      transform       = cov_matrix(),
      original_coords = TRUE
    )

>>>>

observeEvent(
  list(input$a_1, input$a_2, input$d, cov_matrix()),
  item_oblique({
    oblique_params <- item_M2PL() |> compute_mirt_params(
      all_of(INTERCEPT_COLKEY), starts_with(DISCR_PREFFIX), # Input parameters
      cov_matrix = cov_matrix(),                            # Input covariance
      dir_out    = c(COSINE_DIRTYPE, DEGREE_DIRTYPE)        # Output config.
    )
    oblique_coords <- oblique_params |> compute_mirt_coords(
      D, MDISC, starts_with(COSINE_DIRTYPE),
      transform       = cov_matrix(),
      original_coords = TRUE
    )
